
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.6 in,top=0.7in,right=0.6 in,bottom=0.4in]{geometry} % Document margins
\usepackage{setspace}
\spacing{0.90}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ayush Sachan} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address {\href{https://ayushsachan.in@gmail.com}{ayushsachan.in@gmail.com} \\ 
{+91-8840733668 }\\
\href{https://www.linkedin.com/in/ayush-sachan-469124234/}{linkedin.com/in/ayush-sachan} \\ \href{https://github.com/ayushsachan123}{github.com/ayushsachan123}}  %

\begin{document}

\begin{rSection}{Education}
{\bf Bachelor of Technology, Krishna Group of Institution, Gaziabad},  \hfill {\textit{2021-Present}}\\
Major. Computer Science and Engineering \hfill {\textit{CGPA(after 2 semesters): 7.8/10}}

{\bf Subhash Public School, Kanpur} \hfill {\textit{2020 - 2021}} \\
Senior Secondary(Class 12) \hfill {\textit{CBSE: 81\%}} 

{\bf Subhash Public School, Kanpur} \hfill {\textit{2018 - 2019}} \\
Senior Secondary(Class 10) \hfill {\textit{CBSE: 89\%}} 

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages: &[C++, C, Javascript](Most Experience). [Java, Python](Some experience).\\
Web Development: &HTML, CSS, Bootstrap, JQuery, Node.js, MySQL, MongoDB, Mongoose, React.js.\\
IDEs and Tools: & Visual Studio, Sublime Text, Eclipse, Atom, Git, GitHub, Docker, Heroku, Cyclic.  \\

\end{tabular}\\
\end{rSection}

\begin{rSection}{POSITIONS OF RESPONSIBILITY}

\textbf{Team Member} \hfill \textit{mar 2022 - Present}\\
DSC KIET \hfill \textit{KIET Gaziabad}
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf {Web Developer,} Resposible for deploying various Club's websites and projects.
 \end{itemize}
 
\textbf{Squad Member} \hfill \textit{july 2022 - Present}\\
Mood Indigo \hfill \textit{IIT Bombay}
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf {Contingent Leader,} Represent our college in mood indigo occured at IIT Bombay.

 \end{itemize}

 \textbf{Team Member} \hfill \textit{November 2022 - Present}\\
Advance Learner Group \hfill \textit{KIET Gaziabad}
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf {Competitive Programmer,} Practice DSA questions in Leetcode, Codeforces etc.

 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\textbf{Choosing innovations | Innotech-22 Inter Institute Technical Fest | KIET Gaziabad} \hfill \href{https://github.com/ayushsachan123}{\underline{(GitHub)}} 
\begin{itemize}
    \item Designed and built a website for people in rural areas where technology are not provided.
    \item It's type of giving feedback and choosing which types of services people there are wanting to adapt.
    \item Used various technologies like HTML5, CSS, Bootstrap, Javascript.
\end{itemize}
\textbf{Simon Game} \hfill \href{https://github.com/ayushsachan123}{\underline{(GitHub)}} 
\begin{itemize}
\item It is the exiting electronic game of lights and sounds.
\item In this the players must repeat random sequences of lights by pressing the colored pads in the correct order.
\item Used various technologies like HTML5, CSS, Bootstrap, Javascript.
\end{itemize}
\textbf{Movie Recommender} \hfill \href{https://github.com/ayushsachan123}{\underline{(GitHub)}}
\begin{itemize} 
    \item It recommends the movie according to the movie rating, votes,Word wide collection.
    \item Used various technologies like HTML5, CSS, Bootstrap, Javascript.
\end{itemize}
\end{rSection} 


%----------------------------------------------------------------------------------------
\begin{rSection}{RELEVENT COURSEWORK} 
\begin{itemize}
    \item Data Structures and Algorithms, Computer Organization, Mathematics for Computer Science, Linear Algebra, Object-Oriented Programming, Information and Database Systems.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{ACHIEVEMENTS} 
\begin{itemize}
 \item Ranked 5 star on \href{https://www.hackerrank.com/ayushsachan_in}{HackerRank/@ayushsachan} and 2 star on \href{https://www.codechef.com/users/ayushsachan123}{Codechef/ayushsachan123}. \hfill \textit{December 2022}
 \item \textbf{Stood 3th} in 1st year’s competitive programming contest, KIET Gaziabad. \hfill \textit{November 2021}
 \item 1500+ contributions at \href{https://github.com/ayushsachan123}{(GitHub)}\hfill \textit{February 2023}
 \item Java Project Certificate from College\hfill \textit{September 2022}
\end{itemize}


\end{rSection}


\end{document}

